\(ler\) : LVK (LIGO-Virgo-KAGRA collaboration) event (compact-binary mergers) rate calculator and simulator

### 2024-07-03 arxiv/paper.tex
mac

\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Phurailatpam Hemantakumar, Anupreeta More, Harsh Narola, Ng Chung Yin (Leo), Justin Janquart, Chris Van Den Broeck, Otto Akseli HANNUKSELA, Neha Singh, and David Keitel, (2024). \(ler\)
: LVK (LIGO-Virgo-KAGRA collaboration) event (compact-binary mergers)
rate calculator and
simulator. \textit{Journal of Open Source Software}, (), . \url{https://doi.org/10.xxxxxx/draft}}}}

@@

        \author[1]{Phurailatpam Hemantakumar}
          \author[2,3]{Anupreeta More}
          \author[4,5]{Harsh Narola}
          \author[1]{Ng Chung Yin (Leo)}
          \author[4,5,6,7]{Justin Janquart}
          \author[4,5]{Chris Van Den Broeck}
          \author[1]{Otto Akseli Hannukkala}
          \author[8]{Neha Singh}
          \author[8]{David Keitel}

@@

  {\bfseries Submitted:} 19 June 2024\\
  {\bfseries Published:} 19 June 2024

@@

Gravitational waves (GWs) are ripples in the fabric of space and time
caused by the acceleration of unevenly distributed mass or masses.
Observable GWs are created especially during the violent cosmic events
of merging compact binaries, such as `binary black holes' (BBHs),
`binary neutron stars' (BNSs), and `neutron star and black hole pair'
(NSBHs). GWs emitted by these events can be distorted or magnified by
the gravitational fields of massive objects such as galaxies or galaxy
clusters, a phenomenon known as gravitational lensing. Profound
comprehension of gravitational lensing's impact on GW signals is
imperative to their accurate interpretation and the extraction of
astrophysical insights therein. For this purpose, statistical modelling
of GWs lensing can provide valuable insights into the properties of the
lensing objects and GW sources. Such statistics require accurate and
efficient means to calculate the detectable lensing rates, which depend
on up-to-date modeling and implementation of lens and source properties
and their distribution. The outcomes of these computational analyses not
only contribute to generating dependable forecasts but also play an
important role in validating forthcoming lensing events (Janquart et al.
2023).

@@

The authors express their sincere appreciation for the significant
contributions that have been instrumental in completing this research.
Special thanks are extended to the academic advisors for their
invaluable guidance and steadfast support. The collaborative efforts and
enriching discussions with research colleagues significantly enhanced
the study's quality. Acknowledgement is given to the Department of
Physics, The Chinese University of Hong Kong, for the Postgraduate
Studentship that facilitated this research. Further gratitude is
extended to the Netherlands Organisation for Scientific Research (NWO)
for their support. The authors also recognize the contributions of
individuals who added empirical depth to this work. Appreciation is
conveyed for the computational resources provided by the LIGO
Laboratory, supported by National Science Foundation Grants
No.~PHY-0757058 and No.~PHY-0823459. N. Singh and D. Keitel are
supported by Universitat de les Illes Balears (UIB); the Spanish Agencia
Estatal de Investigación grants CNS2022-135440, PID2022-138626NB-I00,
RED2022-134204-E, RED2022-134411-T, funded by
MICIU/AEI/10.13039/501100011033, the European Union
NextGenerationEU/PRTR, and the ERDF/EU; and the Comunitat Autònoma de
les Illes Balears through the Direcció General de Recerca, Innovació I
Transformació Digital with funds from the Tourist Stay Tax Law
(PDR2020/11 - ITS2017-006) as well as through the Conselleria
d'Economia, Hisenda i Innovació with grant numbers SINCO2022/6719
(European Union NextGenerationEU/PRTR-C17.I1) and SINCO2022/18146
(co-financed by the European Union and FEDER Operational Program
2021-2027 of the Balearic Islands).

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-VIRGO2015}
Acernese, F, M Agathos, K Agatsuma, D Aisa, N Allemandou, A Allocca, J
Amarni, et al. 2014. {``Advanced Virgo: A Second-Generation
Interferometric Gravitational Wave Detector.''} \emph{Classical and
Quantum Gravity} 32 (2): 024001.
\url{https://doi.org/10.1088/0264-9381/32/2/024001}.

@@

>>>>

\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Hemantakumar Phurailatpam , Anupreeta More, Harsh Narola, Ng Chung Yin (Leo), Justin Janquart, Chris Van Den Broeck, Otto Akseli Hannukkala, Neha Singh, and David Keitel, (2024). \(ler\)
: LVK (LIGO-Virgo-KAGRA collaboration) event (compact-binary mergers)
rate calculator and
simulator. \textit{Journal of Open Source Software}, (), . \url{https://doi.org/10.xxxxxx/draft}}}}

@@

        \author[1]{Hemantakumar Phurailatpam}
          \author[2,3]{Anupreeta More}
          \author[4,5]{Harsh Narola}
          \author[1]{Ng Chung Yin (Leo)}
          \author[4,5,6,7]{Justin Janquart}
          \author[4,5]{Chris Van Den Broeck}
          \author[1]{Otto Akseli Hannukkala}
          \author[8]{Neha Singh}
          \author[8]{David Keitel}

@@

  {\bfseries Submitted:} 3rd July 2024\\
  {\bfseries Published:} 3rd July 2024

@@

Gravitational waves (GWs) are ripples in the fabric of space and time
caused by the acceleration of unevenly distributed mass or masses.
Observable GWs are created especially during the violent cosmic events
of merging compact binaries, such as `binary black holes' (BBHs),
`binary neutron stars' (BNSs), and `neutron star and black hole pair'
(NSBHs). GWs emitted by these events can be distorted or magnified by
the gravitational fields of massive objects such as galaxies or galaxy
clusters, a phenomenon known as gravitational lensing. Profound
comprehension of gravitational lensing's impact on GW signals is
imperative to their accurate interpretation and the extraction of
astrophysical insights therein. For this purpose, statistical modelling
of GWs lensing can provide valuable insights into the properties of the
lensing objects and GW sources. Such statistics require accurate and
efficient means to calculate the detectable lensing rates, which depend
on up-to-date modeling and implementation of lens and source properties
and their distribution. The outcomes of these computational analyses not
only contribute to generating dependable forecasts but also play an
important role in validating forthcoming lensing events (Janquart et al.
2023) (Collaboration et al. 2023) (Abbott et al. 2021).

@@

The authors express their sincere appreciation for the significant
contributions that have been instrumental in completing this research.
Special thanks are extended to the academic advisors for their
invaluable guidance and steadfast support. Acknowledgement is given to
the Department of Physics, The Chinese University of Hong Kong, for the
Postgraduate Studentship that facilitated this research. Hemantakumar
Phurailatpam and Otto A. Hannuksela acknowledge support by grants from
the Research Grants Council of Hong Kong (Project No.~CUHK 14304622 and
14307923), the start-up grant from the Chinese University of Hong Kong,
and the Direct Grant for Research from the Research Committee of The
Chinese University of Hong Kong. Further gratitude is extended to the
Netherlands Organisation for Scientific Research (NWO) for their
support. N. Singh and D. Keitel are supported by Universitat de les
Illes Balears (UIB); the Spanish Agencia Estatal de Investigación grants
CNS2022-135440, PID2022-138626NB-I00, RED2022-134204-E,
RED2022-134411-T, funded by MICIU/AEI/10.13039/501100011033, the
European Union NextGenerationEU/PRTR, and the ERDF/EU; and the Comunitat
Autònoma de les Illes Balears through the Direcció General de Recerca,
Innovació I Transformació Digital with funds from the Tourist Stay Tax
Law (PDR2020/11 - ITS2017-006) as well as through the Conselleria
d'Economia, Hisenda i Innovació with grant numbers SINCO2022/6719
(European Union NextGenerationEU/PRTR-C17.I1) and SINCO2022/18146
(co-financed by the European Union and FEDER Operational Program
2021-2027 of the Balearic Islands). The authors also recognize the
contributions of individuals who added empirical depth to this work.
Appreciation is conveyed for the computational resources provided by the
LIGO Laboratory, supported by National Science Foundation Grants
No.~PHY-0757058 and No.~PHY-0823459.

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-Abbott2021}
Abbott, R., T. D. Abbott, S. Abraham, F. Acernese, K. Ackley, A. Adams,
C. Adams, et al. 2021. {``Search for Lensing Signatures in the
Gravitational-Wave Observations from the First Half of LIGO--Virgo's
Third Observing Run.''} \emph{The Astrophysical Journal} 923 (1): 14.
\url{https://doi.org/10.3847/1538-4357/ac23db}.

\bibitem[\citeproctext]{ref-VIRGO2015}
Acernese, F, M Agathos, K Agatsuma, D Aisa, N Allemandou, A Allocca, J
Amarni, et al. 2014. {``Advanced Virgo: A Second-Generation
Interferometric Gravitational Wave Detector.''} \emph{Classical and
Quantum Gravity} 32 (2): 024001.
\url{https://doi.org/10.1088/0264-9381/32/2/024001}.

@@

\bibitem[\citeproctext]{ref-ligolensing2023}
Collaboration, The LIGO Scientific, the Virgo Collaboration, the KAGRA
Collaboration, R. Abbott, H. Abe, F. Acernese, K. Ackley, et al. 2023.
{``Search for Gravitational-Lensing Signatures in the Full Third
Observing Run of the LIGO-Virgo Network.''}
\url{https://arxiv.org/abs/2304.08393}.
